# R Code

- `print()`, `cat()`
- typing in the terminal, `source`, Rscript
- Comments

## Assigned Reading

- [R4DS Sections 1.4-1.6](http://r4ds.had.co.nz/introduction.html#prerequisites)


## How Computers Execute Code

The following notes are based upon the first chapter of @gaddis.

Figure 1-8 from @gaddis:

1. Clearly define what the program is to do.
2. Visualize the program running on the computer.
3. Use design tools such as a hierarchy chart, flowcharts, or pseudocode to
   create a model of the program.
4. Check the model for logical errors.
5. Type the code, save it, and compile it.
6. Correct any errors found during compilation. Repeat steps 5 and 6 as many
   times as necessary.
7. Run the program with test data for input.
8. Correct any errors found while running the program. Repeat steps 5 through 8
   as many times as necessary.
9. Validate the results of the program.

Some slight  modifications are needed for interpretted languages like R. The
"compile it" part of step 5 does not apply to most things you do in R, and you
will typically combine steps 5 and 7 into "Type, the code, save it, and run it
with test data for input." Steps 6 and 8 also occur at the same time, but are
conceptually different. Step 6 is about making sure your code makes sense to
the computer; step 8 is about making sure the computer interprets your code the
way you intended.


## Running R Code from Source Files

The file [`examples/intro_example.r`](examples/intro_example.r) contains the following code.

```{r engine = 'bash', echo = FALSE, comment = NA}
cat examples/intro_example.r
```

In the R terminal, use the `source()` command to run the code in the file. This
command is an example of a _function_, or block of code that is reused by
calling its name. The text in parentheses are inputs to the function, called
_arguments_. The first argument (in quotes) is the name of the source file to
read. The second argument, `print.eval = TRUE`, tells R to print out the
results of any expressions in the source file. We will learn much more about
functions in Section 5.

```{r}
source('examples/intro_example.r', print.eval = TRUE)
```

From the system terminal or command prompt, you can use the `Rscript` command
execute R code saved in a file.

```{r engine = 'bash'}
Rscript examples/intro_example.r
```


## Exercises

1. The traditional first program written by students in a computer programming
  course is `Hello World!`, which simply prints the text "Hello World!" on the
  screen. Write R code to output "Hellow World!" (or something similar), save
  the code in a `.r` file, and run the file using either `source()` or
  `Rscript`.
