# R Code

- `print()`, `cat()`
- typing in the terminal, `source`, Rscript
- Comments

## Assigned Reading

- [R4DS Sections 1.4-1.6](http://r4ds.had.co.nz/introduction.html#prerequisites)


## How R Executes Code


## Running R Code from Source Files

The file [`examples/intro_example.r`](examples/intro_example.r) contains the following code.

```{r engine = 'bash', echo = FALSE}
cat examples/intro_example.r
```

In the R terminal, use the `source()` command to run the code in the file. This
command is an example of a _function_, or block of code that is reused by
calling its name. The text in parentheses are inputs to the function, called
_arguments_. The first argument (in quotes) is the name of the source file to
read. The second argument, `print.eval = TRUE`, tells R to print out the
results of any expressions in the source file. We will learn much more about
functions in Section 5.

```{r}
source('examples/intro_example.r', print.eval = TRUE)
```

From the system terminal or command prompt, you can use the `Rscript` command
execute R code saved in a file.

```{r engine = 'bash'}
Rscript examples/intro_example.r
```


## Exercises

1. The traditional first program written by students in a computer programming
  course is `Hello World!`, which simply prints the text "Hello World!" on the
  screen. Write R code to output "Hellow World!" (or something similar), save
  the code in a `.r` file, and run the file using either `source()` or
  `Rscript`.
